---
title: "Air Quality Time Series"
author: "hangulandy"
date: "7/3/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Executive Summary

This project attempts to show airquality features as a time series using the plotly package to create an interactive graph.

## Data

The data used for this project are the airquality data that come with the datasets package. 

```{r}
dat <- airquality
```

## Impute Missing Data

### NA Values

As seen here, there are only two features with missing values.

```{r}
apply(apply(dat, 2, is.na), 2, sum)
```

I used the median feature value to impute missing values in order to retain all available days in the time series.

```{r}
for (i in 1:ncol(dat)) {
        if(sum(is.na(dat[, i])) > 0) {
                temp <- median(dat[, i], na.rm = TRUE)
                dat[is.na(dat[, i]), i] <- temp
        }
}
```

## Making the Time Series

### Building the Date

In order to make the time series data, I had to create a date with existing data.  The dataset comes from data in 1973 (according to the documentation).

```{r}
dat$Year <- as.integer(1973)
dat$Dt <- paste(dat$Month , dat$Day , dat$Year, sep = ".")
library(lubridate)
dat$Dt <- mdy(dat$Dt)
```

### Collapsing to Key Values

```{r}
library(tidyr)
dat <- gather(dat, index, measure, 1:4)
```

## Plot the Time Series

```{r}
library(plotly)
with(dat, plot_ly(x = Dt, y = measure, mode = "lines", color = index))
```

# Thank You!

